### 2023-08-03 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
yny

Under a linear shear flow, a multicomponent vesicle exhibits more exotic dynamics in both shape and membrane composition \cite{soh-tse-li-voi-low2010, Smith2007_JChemPhys,Cox2015_Nonlinearity,Liu2017_SoftMatter,Tusch2018_PRF,Gera2018_SoftMatter,ger-sal-spa2022} than a single-component vesicle.
For example, multicomponent vesicles under a background flow often exhibit highly complex morphologies, leading to vesicle budding. 
The hydrodynamics of these
multicomponent vesicles include phase treading, tumbling with no
viscosity contrast, swinging, budding, and
fission~\cite{soh-tse-li-voi-low2010, wan-du2008, all-ama2006,
ger-sal-spa2022, lip1992, urs-klu-phi2009}. In addition to the
aforementioned numerical studies, these dynamics have been observed in
experiments~\cite{bag-sun2009, yan-ima-tan2010, yan-ima-tan2008,
dre-jah-bob-spa-gop2021}.

@@

Hydrodynamics of vesicles in extreme confinement has been studied as a model system for red blood cells (RBCs) squeezing through small
capillaries (of sub-micron size in diameter) under a pressure difference \cite{LuPeng2019_PoF,gur-pak-tay-siv-sac2023}. Membrane permeability has been incorporated to examine the single-component vesicle hydrodynamics. In the absence of an osmotic gradient, the semipermeable vesicle is affected by water influx/efflux over a sufficiently long time or under a strong confinement \cite{qua-gan-you2021}. Numerical simulations illustrate that a vesicle with moderate membrane permeability can go through a strong confinement much more easily, and can restore its water content within a very short time after its passage through the strong confinement \cite{qua-gan-you2021}.  These results imply that the membrane permeability may be inferred from vesicle hydrodynamics under a strong confinement.  Motivated by these results, in this work we seek to investigate how strong confinement may affect the hydrodynamics of a multi-component vesicle? This question is highly relevant to hydrodynamics of cells in a confinement, and to our knowledge has not been well studied.

In this paper, we extend the work of Liu et
al.~\cite{liu-mar-li-vee-low2017} who performed a thorough investigation
of how key dimensionless numbers, including the reduced area, capillary
number, and the floppy-to-stiff ratio, affect the dynamics of a
multicomponent vesicle in an unbounded linear shear flow. What is
missing from the literature, and what we address in this work, is the
effect of strong confinement on a two-dimensional multicomponent
vesicle. Using numerical simulations, we show how the vesicle's reduced
area and its lipid composition affect the dynamics in two strongly
confined geometries.

The remainder of the paper is organized as follows.
Section~\ref{sec:Formulation} describes the model for the
two-dimensional multicomponent vesicle. We introduce a new
parameterization of the bending modulus that is necessary to avoid
unphysical negative bending stiffness.
Section~\ref{sec:NumericalMethods} describes numerical methods and also
defines the techniques we use to define the excess pressure, lubrication
layer width, and tank treading velocity. Section~\ref{sec:results}
demonstrates the effects of strong confinement on multicomponent
vesicles. Finally, concluding remarks are made in
Section~\ref{sec:conclusion}.

@@

\citet{ram-kom-sek-ima2010}

\citet{che-lyu-jae-leo2020}

@@

\citet{mis-wis-ber-key-li-tun-law-per-erd-zha-zha-sun-kal-lam-kon2019}
is paper with Sean Sun that looks at linear and non-linear shear in the
boundary layer caused by tank treading behavior.

>>>>

Under a linear shear flow, a multicomponent vesicle exhibits more exotic dynamics in both shape and membrane composition \cite{soh-tse-li-voi-low2010, Smith2007_JChemPhys,Cox2015_Nonlinearity,liu-mar-li-vee-low2017,Tusch2018_PRF,Gera2018_SoftMatter,ger-sal-spa2022} than a single-component vesicle.
For example, multicomponent vesicles under a background flow often exhibit highly complex morphologies, leading to vesicle budding. 
The hydrodynamics of these
multicomponent vesicles include phase treading, tumbling with no
viscosity contrast, swinging, budding, and
fission~\cite{soh-tse-li-voi-low2010, wan-du2008, all-ama2006,
ger-sal-spa2022, lip1992, urs-klu-phi2009}. 
Through numerical investigations, 
Liu {\it et al.}~\cite{liu-mar-li-vee-low2017} identified several key dimensionless numbers, including the reduced area, capillary
number, and the floppy-to-stiff ratio to characterize various dynamics of a
multicomponent vesicle in an unbounded linear shear flow. In addition to the
aforementioned numerical studies, these dynamics have been observed in
experiments~\cite{bag-sun2009, yan-ima-tan2010, yan-ima-tan2008,
dre-jah-bob-spa-gop2021}.

@@

Hydrodynamics of vesicles in extreme confinement has been studied as a model system for red blood cells (RBCs) squeezing through small
capillaries (of sub-micron size in diameter) under a pressure difference \cite{LuPeng2019_PoF,che-lyu-jae-leo2020,gur-pak-tay-siv-sac2023}. Membrane permeability has been incorporated to examine the single-component vesicle hydrodynamics. In the absence of an osmotic gradient, the semipermeable vesicle is affected by water influx/efflux over a sufficiently long time or under a strong confinement \cite{qua-gan-you2021}. Numerical simulations illustrate that a vesicle with moderate membrane permeability can go through a strong confinement much more easily, and can restore its water content within a very short time after its passage through the strong confinement \cite{qua-gan-you2021}.  These results imply that the membrane permeability may be inferred from vesicle hydrodynamics under a strong confinement.  Motivated by these results, in this work we seek to investigate how strong confinement may affect the hydrodynamics of a multi-component vesicle? This question is highly relevant to hydrodynamics of cells in a confinement, and to our knowledge has not been well studied. 
Ramachandran {\it et al.} \cite{ram-kom-sek-ima2010} reported that confinement reduces the effective diffusion coefficient of the concentration fluctuation in multicomponent membranes. How is such reduced concentration diffusion coefficient reflected in the hydrodynamics of multicomponent vesicles under strong confinement?

In this paper, we use numerical simulations and lubrication analysis \cite{mis-wis-ber-key-li-tun-law-per-erd-zha-zha-sun-kal-lam-kon2019} 
to investigate the effect of strong confinement on a multicomponent vesicle.
In particular we show how the vesicle's reduced
area and its lipid composition affect the dynamics in two strongly
confined geometries.
%
The remainder of the paper is organized as follows.
Section~\ref{sec:Formulation} describes the model for the
two-dimensional multicomponent vesicle. We introduce a new
parameterization of the bending modulus that is necessary to avoid
unphysical negative bending stiffness.
Section~\ref{sec:NumericalMethods} describes numerical methods and also
defines the techniques we use to define the excess pressure, lubrication
layer width, and tank treading velocity. Section~\ref{sec:results}
demonstrates the effects of strong confinement on multicomponent
vesicles. Finally, concluding remarks are made in
Section~\ref{sec:conclusion}.

@@

@@

%\citet{mis-wis-ber-key-li-tun-law-per-erd-zha-zha-sun-kal-lam-kon2019}
%is paper with Sean Sun that looks at linear and non-linear shear in the
%boundary layer caused by tank treading behavior.
